Conceptual and methodological problems with bias detection and avoidance in natural language processing

### 2021-06-08 thesis/_book/_main.tex
datasets upload

---
output:
  pdf_document: default
  html_document: default
---
# Introduction

<!--### Articles:

  1. "Are We Consistently Biased? Multidimensional Analysis of Biases in Distributional Word Vectors"
  https://www.aclweb.org/anthology/S19-1010.pdf

  2. Proving the harmfullness of biases in models 
[source https://poseidon01.ssrn.com/delivery.php?ID=004020091089126117028081015085009075120015077012021005105005104113074127101113104030041107053119007034112081087110119071025006053026022082043000071011123067077124004027040024008122116091025075126111098104007096110113089007070120009111119015084097017092&EXT=pdf&INDEX=TRUE]

  3. Summary what causes bias short article
  [source https://kawine.github.io/blog/nlp/2019/09/23/bias.html]-->

<!-- Men Also Like Shopping: Reducing Gender Bias Amplification using Corpus-level Constraint -->
<!-- Bias in Bios: A Case Study of Semantic Representation Bias in a High-Stakes Setting -->

<!-- !bibliografia paperdraft; jabref
4.pomysly na czwarty rozdzial - podsumowanie; 
jak mierzyc bias za pomoca jednej liczby?
IAT - test psychologiczny -->

<!-- 
    1.state the general topic and give some background
    2.provide a review of the literature related to the topic
    3.define the terms and scope of the topic
    4.outline the current situation
    5.evaluate the current situation (advantages/ disadvantages) and identify the gap
    6.identify the importance of the proposed research
    7.state the research problem/ questions
    8.state the research aims and/or research objectives
    9.state the hypotheses
    10.outline the order of information in the thesis
    11.outline the methodology
-->

@@

<!-- Nissim2019Fair -->

@@

>>>>

\documentclass[]{book}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdftitle={Conceptual and methodological problems with bias detection and avoidance in natural language processing},
            pdfauthor={Alicja Dobrzeniecka},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
% Fix footnotes in tables (requires footnote package)
\IfFileExists{footnote.sty}{\usepackage{footnote}\makesavenoteenv{long table}}{}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\title{Conceptual and methodological problems with bias detection and avoidance
in natural language processing}
\author{Alicja Dobrzeniecka}
\date{2021-06-08}

\begin{document}
\maketitle

{
\setcounter{tocdepth}{5}
\tableofcontents
}
\chapter*{Preface}\label{preface}
\addcontentsline{toc}{chapter}{Preface}

Test

\chapter{Introduction}\label{introduction}

@@

@@

\end{document}
